First and foremost, I would like to thank my adviser Anne Schilling for her guidance during my years in graduate school and for her patience during my last year. 
My career and research goals changed drastically during the last few years, and I am very grateful for her continued support.

I also wish to thank James Sharpnack, who introduced me to machine learning research. 
James helped me to find a direction to move forward, his energy and enthusiasm fueled my last year in the school.

I would like to thank Eugene Gorsky for suggesting an interesting combinatorial problem, which resulted in Chapter~\ref{ch:fibonacci}, and for helpful discussions.
I would also like to thank my co-author Graham Hawkes, who did a lot of theoretical work for Chapter~\ref{ch:crystals}.

I am grateful to many professors in UC Davis: Monica Vazirani, Greg Kuperberg, Fu Liu and Dan Romik for interesting courses and discussions during the first two years of the school, and for helping me with the Qualifying exam; Thomas Strohmer and Mimi Tsuruga for introducing me to Data Science; Alexander Soshnikov for guidance at the beginning of the program.

I would like to thank the staff of Mathematics Department, in particular Tina Denena and Sarah Driver for tremendous help and support. Last but not least, I wish to thank my fellow graduate students, in particular my office mate Robert Bassett, for keeping me sane.

My research was financially supported by Mathematics Department and NSF grant DMS-1500050.

I am very grateful for my time in UC Davis.
I have met many great people here and I hope I can maintain a connection with UC Davis long after my graduation.